Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-06-10 paper/long_version.tex
Auto Update from local Sharelatex

Brief explaination of each method.

hmm, that's interesting

>>>>

\begin{table}
  \caption{Kung Faux Pandas data synthesis plugin timings (seconds)}
  \label{timing_results}
  \centering
    \begin{tabular}{l c c c c c}
    	\toprule 
    	Method & 10 rows & 100 rows & 1000 rows & 10000 rows & 100000 rows\\ 
    	\midrule 
    	Trivial & x.y (1.04) & x.y (1.04) &  &  &  \\ 
    	KDE & x.y (1.04) &  & x.y (1.04) &  &  \\ 
    	DS Correlated & x.y (1.04) &  &  & x.y (1.04) &  \\ 
    	DS Correlated w/Config & x.y (1.04) &  &  &  & x.y (1.04) \\ 
    	DS Independent & x.y (1.04) &  &  &  &  \\ 
    	DS Independent w/Config & x.y (1.04) &  &  &  & x.y (1.04) \\
    	\midrule
    \end{tabular}
\end{table}

Brief explanation of each method.

hmm, that's interesting. Describe what this means...
